---
title: "Simulation Studies"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulation Studies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This file aims to document the usage of the functions contained in the surveyROC package, as well as the simulation studies using ROC curve for complex survey data.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7.5,
  fig.height = 6
)
```

```{r setup}
library(surveyROC)
```

# Stratified Simple Random Sampling

## Function Usage

First, specify the parameters for the finite population:

```{r param_pop}
N = 100000
p1 = .25

param_pop <- 
  data.frame(
    strata = 1:10,
    prob = c(.01, .02, .03, .04, .05, .10, .15, .2, .2, .2),
    mu0 = rep(0, 10),
    sigma0 = rep(1, 10),
    mu1 = seq(5, .5, by = -.5),
    sigma1 = rep(1, 10)
  )

```

From the parameters specified above, we have the following ROC curves per strata, as well as the curve for the population:

```{r roc_plots}

# Binormal ROC curve per strata
roc_strat <- binormal_roc_strat(seq(0,1,.01),
                                freq_strata = param_pop$prob,
                                mean0_strat = param_pop$mu0,
                                mean1_strat = param_pop$mu1,
                                sigma0_strat = param_pop$sigma0,
                                sigma1_strat = param_pop$sigma1,
                                by_strata = TRUE) 

# Binormal ROC curve for population
roc_pop <- binormal_roc_strat(seq(0,1,.01),
                              freq_strata = param_pop$prob,
                              mean0_strat = param_pop$mu0,
                              mean1_strat = param_pop$mu1,
                              sigma0_strat = param_pop$sigma0,
                              sigma1_strat = param_pop$sigma1)

# Plotting curves
roc_strat %>% 
  ggplot() +
  geom_line(aes(x = x, y = roc, color = factor(strata))) +
  geom_line(aes(x = x, y = roc), data = roc_pop)

```

We can generate a stratified population using the specified parameters by running:

```{r gen_pop}

pop <- generate_pop_strat(N = N,
                          freq_strata = param_pop$prob,
                          mean0_strat = param_pop$mu0,
                          mean1_strat = param_pop$mu1,
                          sigma0_strat = param_pop$sigma0,
                          sigma1_strat = param_pop$sigma1,
                          p1 = p1)

glimpse(pop)
```

We can check the estimated ROC curve for the generated population:

```{r }

# Nesting population by strata
pop_nest <-
  pop %>%
  group_by(strata) %>%
  nest()

# Estimating finite population ROC curve per strata 
pop_nest$data %>%
  map_dfr(estimate_survey_roc, .id = 'strata') %>% 
  mutate(strata = as.numeric(strata)) %>% 
  ggplot(aes(x = fpr, y = tpr, color = factor(strata))) +
  geom_step()

```

To generate a sample, we run:

```{r }

# Stratified SRS
sample <- 
  pop %>% 
  generate_srs_strat(sample_size = 1000)

# Ploting ROC curve

sample %>% 
  estimate_survey_roc(var_weight = 'weight',
                    ci = TRUE) %>% 
  ggplot(aes(x = fpr)) +
  geom_step(aes(y = tpr)) +
  geom_step(aes(y = tp_ci_l)) +
  geom_step(aes(y = tp_ci_u))+
  geom_line(aes(x = x, y = roc), data = roc_pop, color = 'red')

```

## Simulation Studies

```{r sim}

sim1 <-
  simulate_strat(N_pop = 10,
               pop_size = 100000,
               param_pop = param_pop,
               prop_disease = p1,
               N_sample = 1000,
               sample_size = 1000,
               grid = seq(0, 1, by=0.1))

sim2 <-
  simulate_strat(N_pop = 2,
               pop_size = 100000,
               param_pop = param_pop,
               prop_disease = p1,
               N_sample = 2,
               sample_size = 1000,
               grid = seq(0, 1, by=0.1))

sim3 <-
  simulate_strat(N_pop = 2,
               pop_size = 100000,
               param_pop = param_pop,
               prop_disease = p1,
               N_sample = 2,
               sample_size = 1000,
               grid = seq(0, 1, by=0.1))

compute_sim_quant(sim, param_pop)

```
